---
title: "GBOP2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Installation

The R package **GBOP2** is available for free on the Comprehensive R Archive Network (CRAN). It offers functions for implementing G-BOP2 design with various Particle Swarm Optimization (PSO) algorithms, including PSO-Default, PSO-Quantum, PSO-DEXP, and PSO-GO. The package can be loaded with the following command:


```{r}
# install.packages("GBOP2")
library(GBOP2)
```



## Summary of functions

|                          | Single Boundary        |  Dual Boundary      | Toxicity and Efficacy|
|--------------------------|------------------------|--------------------------|-----------------|
| Sample Size Minimization | GBOP2_minSS_single |  GBOP2_minSS_dual |GBOP2_minSS_TE|
| Power Maximization       | GBOP2_maxP_single  |  GBOP2_maxP_dual  |GBOP2_maxP_TE |


## Single boundary - futility monitoring only

#### Sample size minimization
The `GBOP2_minSS_single` function is designed to identify the optimal and minimax designs for single futility boundary, which meets the pre-specified Type I and Type II error rates by using PSO_GO algorithm. Parameters such as `nlooks`, `weight`, `maxPatients`, `Nmin_cohort1`, and `Nmin_increase` provide users with more flexibility to adjust the number of interim looks, the weight of the sample size under the null hypothesis, and other design characteristics. When users choose `pso_method` equals "all", `GBOP2_minSS_single` function conducts PSO_Ensemble in parallel by indicating the number of parallel through `nParallel` option.  Otherwise, users can specify the `pso_method` option as `default`, `quantum`, or `dexp` to conduct a single PSO algorithm. The following two examples show the optimal design identified by the PSO-GO and PSO-default respectively.


```{r, message=FALSE, warning=FALSE}
## PSO-GO
optimal_GO_single <- GBOP2_minSS_single(design = "optimal",
                  nlooks = 1,
                  b1n = 0.2,
                  b1a = 0.4,
                  err1 = 0.05,
                  nParallel = 3,
                  minPower = 0.8,
                  weight = 1,
                  maxPatients = 50,
                  Nmin_cohort1 = 10,
                  Nmin_increase = 5,
                  pso_method = "all",
                  seed = 1024,
                  nSwarm = 64,
                  maxIter = 200,
                  nCore = 4)

summary(optimal_GO_single)
```


```{r, message=FALSE, warning=FALSE}
## PSO-default
optimal_single <- GBOP2_minSS_single(design = "optimal",
                  nlooks = 1,
                  b1n = 0.2,
                  b1a = 0.4,
                  err1 = 0.05,
                  nParallel = 3,
                  minPower = 0.8,
                  weight = 1,
                  maxPatients = 50,
                  Nmin_cohort1 = 10,
                  Nmin_increase = 5,
                  pso_method = "default",
                  nSwarm = 64,
                  maxIter = 200,
                  nCore = 4)

summary(optimal_single)
```


#### Power Maximization
The `PSOGO_power` function is designed to identify the design which maximizing the power for a single futility boundary, which meets the pre-specified Type I and Type II error rates by using PSO_GO algorithm. The parameters are the same as in the `GBOP2_minSS_single` function except for the `totalPatients`, which represents the total number of patients. Similarly, when users choose `pso_method` equals "all", `GBOP2_maxP_single` function conducts PSO_Ensemble in parallel by indicating the number of parallel through `nParallel` option.  Otherwise, users can specify the `pso_method` option as `default`, `quantum`, or `dexp` to conduct a single PSO algorithm. The following two examples show the design maximizes the power identified by the PSO-GO and PSO-default respectively.

```{r, warning=FALSE}
## PSO-GO
power_GO_single <- GBOP2_maxP_single(
    nlooks = 1,
    b1n = 0.2,  # Null hypothesis response rate
    b1a = 0.4,  # Alternative hypothesis response rate
    err1 = 0.05,  # Type I error rate
    nParallel = 3,
    minPower = 0.8, ## power
    weight = 1, ## weight of sample size under null
    totalPatients = 50,  ## maximum number of patients
    Nmin_cohort1 = 10,
    Nmin_increase = 5,
    pso_method = "all", ## three different pso or three single pso
    seed = 1024,
    nSwarm = 64,
    maxIter = 200,
    nCore = 4)

summary(power_GO_single)
```


```{r, warning=FALSE}
## PSO-default
power_single <- GBOP2_maxP_single(
    nlooks = 1,
    b1n = 0.2,  # Null hypothesis response rate
    b1a = 0.4,  # Alternative hypothesis response rate
    err1 = 0.05,  # Type I error rate
    nParallel = 3,
    minPower = 0.8, ## power
    weight = 1, ## weight of sample size under null
    totalPatients = 50,  ## maximum number of patients
    Nmin_cohort1 = 10,
    Nmin_increase = 5,
    pso_method = "default", ## three different pso or three single pso
    seed = 1024,
    nSwarm = 64,
    maxIter = 200,
    nCore = 4)

summary(power_single)
```


## Dual boundary - futility monitoring only

#### Sample size minimization
The `GBOP2_minSS_dual` function is designed to identify the optimal and minimax designs for dual futility boundary, which meets the pre-specified Type I and Type II error rates by using PSO_GO algorithm. When `pso_method` equals "all", `GBOP2_minSS_dual` function conducts PSO_Ensemble in parallel, otherwise, users can specify the `pso_method` option as `default`, `quantum`, or `dexp` to conduct a single PSO algorithm. The following two examples show the optimal design for dual futility boundary identified by the PSO-GO and PSO-default respectively.

```{r, warning=FALSE}
## PSO-GO
optimal_GO_dual <- GBOP2_minSS_dual(
    design = "optimal",
    nlooks = 1,
    b1n = 0.2,
    b1a = 0.4,
    err1 = 0.05,
    nParallel = 3,
    minPower = 0.8,
    weight = 1,
    maxPatients = 50,
    Nmin_cohort1 = 10,
    Nmin_increase = 5,
    pso_method = "all",
    seed = 123,
    nSwarm = 64,
    maxIter = 200,
    nCore = 4)

summary(optimal_GO_dual)
```

```{r, warning=FALSE}
## PSO-default
optimal_dual <- GBOP2_minSS_dual(
    design = "optimal",
    nlooks = 1,
    b1n = 0.2,
    b1a = 0.4,
    err1 = 0.05,
    nParallel = 3,
    minPower = 0.8,
    weight = 1,
    maxPatients = 50,
    Nmin_cohort1 = 10,
    Nmin_increase = 5,
    pso_method = "default",
    seed = 123,
    nSwarm = 64,
    maxIter = 200,
    nCore = 4)

summary(optimal_dual)
```

#### Power Maximization

The `GBOP2_maxP_dual` function is designed to identify the design that maximizing power for dual futility boundary, which meets the pre-specified Type I and Type II error rates by using PSO_GO algorithm. When `pso_method` equals "all", `GBOP2_maxP_dual` function conducts PSO_Ensemble in parallel, otherwise, users can specify the `pso_method` option as `default`, `quantum`, or `dexp` to conduct a single PSO algorithm. The following two examples show the design that maximizing power for dual futility boundary identified by the PSO-GO and PSO-default respectively.

```{r, warning=FALSE}
## PSO-GO
power_GO_dual <- GBOP2_maxP_dual(design = "optimal",
                           nlooks = 1,
                           b1n = 0.2,
                           b1a = 0.4,
                           err1 = 0.05,
                           nParallel = 3,
                           minPower = 0.8,
                           weight = 1,
                           totalPatients = 50,
                           Nmin_cohort1 = 10,
                           Nmin_increase = 5,
                           pso_method = "all",
                           seed = 1024,
                           nSwarm = 64,
                           maxIter = 200,
                           nCore = 4)

summary(power_GO_dual)
```


```{r, warning=FALSE}
## PSO-default
power_dual <- GBOP2_maxP_dual(design = "optimal",
                           nlooks = 1,
                           b1n = 0.2,
                           b1a = 0.4,
                           err1 = 0.05,
                           nParallel = 3,
                           minPower = 0.8,
                           weight = 1,
                           totalPatients = 50,
                           Nmin_cohort1 = 10,
                           Nmin_increase = 5,
                           pso_method = "default",
                           seed = 1024,
                           nSwarm = 64,
                           maxIter = 200,
                           nCore = 4)

summary(power_dual)
```

## Toxicity and Efficacy

#### Sample size minimization
The `GBOP2_minSS_TE` function is designed to identify the optimal and minimax designs for toxicity and efficacy boundary, which meets the pre-specified Type I and Type II error rates by using PSO_GO algorithm. When `pso_method` equals "all", `GBOP2_minSS_dual` function conducts PSO_Ensemble in parallel, otherwise, users can specify the `pso_method` option as `default`, `quantum`, or `dexp` to conduct a single PSO algorithm. The following two examples show the optimal design for dual futility boundary identified by the PSO-GO and PSO-default respectively.

```{r, warning=FALSE}
Optimal_GO_TE <- GBOP2_minSS_TE(design = "optimal",
                            nlooks = 1,
                            skip_efficacy = NULL,
                            skip_toxicity = NULL,
                            maxPatients = 50,
                            Nmin_cohort1 = 10,
                            Nmin_increase = 5,
                            nParallel = 3,
                            e1n = 0.3,
                            e2n = 0.4,
                            e3n = 0.2,
                            e1a = 0.6,
                            e2a = 0.2,
                            e3a = 0.15,
                            err_eff = 0.1,
                            err_tox = 0.1,
                            err_all = 0.05,
                            power_eff = 0.8,
                            power_tox = 0.8,
                            power_all = 0.8,
                            pso_method = "all",
                            nSwarm = 32,
                            maxIter = 100,
                            nCore = 4)

summary(Optimal_GO_TE)
```


```{r, warning=FALSE}
# PSO-default
Optimal_TE <- GBOP2_minSS_TE(design = "optimal",
                            nlooks = 1,
                            skip_efficacy = NULL,
                            skip_toxicity = NULL,
                            maxPatients = 50,
                            Nmin_cohort1 = 10,
                            Nmin_increase = 5,
                            nParallel = 3,
                            e1n = 0.3,
                            e2n = 0.4,
                            e3n = 0.2,
                            e1a = 0.6,
                            e2a = 0.2,
                            e3a = 0.15,
                            err_eff = 0.1,
                            err_tox = 0.1,
                            err_all = 0.05,
                            power_eff = 0.8,
                            power_tox = 0.8,
                            power_all = 0.8,
                            pso_method = "default",
                            nSwarm = 32,
                            maxIter = 100,
                            nCore = 4)

summary(Optimal_TE)
```


#### Power Maximization

The `GBOP2_maxP_TE` function is designed to identify the design that maximizing power for TE boundary, which meets the pre-specified Type I and Type II error rates by using PSO_GO algorithm. When `pso_method` equals "all", `GBOP2_maxP_TE` function conducts PSO_Ensemble in parallel, otherwise, users can specify the `pso_method` option as `default`, `quantum`, or `dexp` to conduct a single PSO algorithm. The following two examples show the design that maximizing power for TE boundary identified by the PSO-GO and PSO-default respectively.

```{r}
## PSO-GO
power_GO_TE <- GBOP2_maxP_TE(design = "optimal",
                         pso_method = "all",
                         nlooks = 4,
                         skip_efficacy = NULL,
                         skip_toxicity = NULL,
                         totalPatients = 50,
                         Nmin_cohort1 = 10,
                         Nmin_increase = 5,
                         nParallel = 3,
                         e1n = 0.3,
                         e2n = 0.4,
                         e3n = 0.2,
                         e1a = 0.6,
                         e2a = 0.2,
                         e3a = 0.15,
                         err_eff = 0.1,
                         err_tox = 0.1,
                         err_all = 0.05,
                         power_eff = 0.8,
                         power_tox = 0.8,
                         power_all = 0.8,
                         nSwarm = 32,
                         maxIter = 100,
                         nCore = 4
          )

summary(power_GO_TE)
```





```{r}
## PSO-optimal
power_TE <- GBOP2_maxP_TE(design = "optimal",
                         pso_method = "default",
                         nlooks = 4,
                         skip_efficacy = NULL,
                         skip_toxicity = NULL,
                         totalPatients = 50,
                         Nmin_cohort1 = 10,
                         Nmin_increase = 5,
                         nParallel = 3,
                         e1n = 0.3,
                         e2n = 0.4,
                         e3n = 0.2,
                         e1a = 0.6,
                         e2a = 0.2,
                         e3a = 0.15,
                         err_eff = 0.1,
                         err_tox = 0.1,
                         err_all = 0.05,
                         power_eff = 0.8,
                         power_tox = 0.8,
                         power_all = 0.8,
                         nSwarm = 32,
                         maxIter = 100,
                         nCore = 4
          )

summary(power_TE)
```

















